%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Kévin} % Your first name
\familyname{Sztern} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Software engineer}
%\address{123 Broadway}{City, State 12345}
%\mobile{(000) 111 1111}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{contact@kevinsztern.fr}
\homepage{kevinsztern.fr}{kevinsztern.fr} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{github.com/chewie}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{I am a 5\textsuperscript{th} year CS student from France, interested in software
%development and teaching it to everyone, looking for an internship in
%software engineering}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title


%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\subsection{Certifications}

\cventry{}{Certified Kubernetes Administrator}{https://training.linuxfoundation.org/certification/verify-certifications}{CKA-1700-0178-0100}{}
{Certified by the Cloud Native Computing Foundation (CNCF) for the deployment and administration of Kubernetes clusters.}

\cventry{}{IPv6 certification}{http://ipv6.he.net/certification}{}{}{The certification involves setting up an IPv6 ready server with various services (HTTP, MTA\ldots), along with
verification of basic IPv6 knowledge.}

\subsection{Computer related}

\cvcomputer{Languages}{C, modern C++, Python, sh, SQL,\\occasional web development}{Systems}{GNU/Linux, Windows, BSD basics}
\cvcomputer{DevOps}{Docker, Kubernetes, Distributed systems,\\ OpenStack, Ansible}{Misc.}{Unix system administration, IPv6 networking,\\security basics, functional programming}

\subsection{Languages}

\cvcomputer{French}{Native speaker}{English}{Fluent (TOEIC: 990)}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Jobs and internships}

\cventry{Jan.2017--Current}{Consultant}{OCTO Technology}{}{}
{Confirmed consultant in the Ops division, specialized in cloud related technologies, Kubernetes, and coaching clients about DevOps transformation.
\newline{}\newline{}
Main missions:
\begin{itemize}
\item Coliposte: Industrialization of the underlying platform for the main event driven parcel logistics applications (Ansible, Mesos, OpenStack, Spark, Kafka)
\item Carrefour: Deployment and industrialization of production Kubernetes cluster, with state of the art features and complete hardening. Contribution to the Azure acs-engine project to add missing features (Ansible, Kubernetes, Azure cloud)
\item Multiple one-off consulting and training missions on automation and cloud related technologies (Docker, CI/CD, Networking)
\item Redaction of a series of articles detailling the inner workings of the TCP/IP network protocols on the OCTO blog.
\end{itemize}}
\cventry{Apr.2016--Dec.2016}{Systems and networks engineer}{Smile}{}{}
{In charge of pre-sales operations for cloud and automation related missions, along with organizing and delivering training sessions. Additionally, in charge of overseeing outsourcing operations, managing a team of 3 persons.}
\cventry{Feb.2015--Aug.2015}{Internship: Byzantine distributed systems}{Infinit}{}{}
{Study and implementation of the state of the art of byzantine state replication algorithms to implement a peer-to-peer filesystem. Contribution to the existing file transfer product.}
\cventry{Jan.2014--Dec.2014}{Teaching assistant}{\textsc{EPITA}}{}{}
{Teaching C, C++ and Unix programming to third year students. In charge of quality assurance for internal processes, along with organization of specialized support lessons for struggling students.}

\cventry{Sep.2013--Jan.2014}{Internship: embedded Android virtualization}{Thales Communications \& Security}{}{}
{Development of a secure virtualized environment for embedded devices. Integration and management of a team of 15 persons around the project, and system administration of the research platform.}

\cventry{Oct.2012--Jul.2012}{Teaching assistant}{\textsc{EPITA}}{}{}
{Teaching advanced OCaml and C to second year students.}

\cventry{Jun.2010--Jul.2010}{Internship: Image processing in Common Lisp}{\textsc{LRDE} (EPITA Research and Development Lab)}{}{}
{Participation on Climb, a generic image processing suite in Common Lisp. In particular, design and development of the image format management layer.}

\cventry{Jun.2009--Jul2009}{Internship: Distributed GPGPU computing}{\textsc{LCMCP} (National Center for Scientific Research)}{}{}
{Architecture of a GPGPU cluster for the HPU4Science project to train artificial neural networks to deconvolution
using particle swarm optimization.}

\subsection{Projects}


\cventry{}{MuffinReader}{http://github.com/Chewie/MuffinReader}{}{}
{A web application for viewing the newsgroups used at EPITA.}

\cventry{}{IPv6 certification}{http://ipv6.he.net/certification}{}{}{The certification involves setting up an IPv6 ready server with various services (HTTP, MTA\ldots), along with
verification of basic IPv6 knowledge.}

\cventry{}{K}{http://k.lse.epita.fr}{}{}{Development of a x86 kernel from scratch.}

\cventry{}{Former president of GConfs}{http://gconfs.fr}{}{}{President of the GConfs student association, dedicated to offering talks and presentations to other students.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2008--2015}{Computer science student}{\textsc{EPITA}}{majoring in machine learning and data analytics}{}{Temporary leave between 2010 and 2012 for health reasons}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cventry{}{Close up and stage magic}{}{}{}{Semi-professional performer for 7 years}

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------

\end{document}